---
title: "Developing Data Products - Shiny Application for Motor Trend Magazine MPG Study"
author: "Manny Joe"
date: "February 27, 2016"
output: ioslides_presentation
---

## DATASET
This Shiny app uses the default "mtcars" dataset installed with R that was extracted from a study conducted by Motor Trend magazine, including MPG and 10 other automobile attributes.
```{r, echo=FALSE}
summary(mtcars)
```

## DATASET PLOT

Here is a descriptive plot of the built-in "mtcars" dataset:

```{r, echo=FALSE}
plot(mtcars)
```

## APPLICATION DESCRIPTION

This Shiny app displays the fuel consumption based on 3 of the 10 aspects studied by Motor Trend:

- No. of Clylinders, 

- Transmission Type, and 

- Available Horsepower.

## INSTRUCTIONS

The App accepts user input for three attributes:

* No. of cylinders, 
* Transmission type, and 
* Available Horsepower

The results will be calculated and displayed in the "results" tab.

* The presentation pitch is available at [RPubs](http://rpubs.com/MannyJoe/Developing-Data-Products)

* The deployed app is available at [Shinyapps.io](https://mannyjoe65.shinyapps.io/Developing-Data-Products)

* The course submission source codes are available at [GitHub](https://github.com/MannyJoe/Developing-Data-Products)
